### 2021-07-31 doc/thesis/chapters/results.tex
vhdl now actually (prev. was HLS)

\begin{figure}%
  \centering
  \subfloat[\centering Overview of ]{{\includegraphics[trim=10 10 10 10,clip, width=0.45\textwidth]{img/matlab/lines_of_code_pie_chart_py_all} }}%
  \\
  %\hspace{\fill}
  \subfloat[\centering HLS]{{\includegraphics[trim=10 10 10 10,clip, width=0.45\textwidth]{img/matlab/lines_of_code_pie_chart_py_hls} }}%
  %\hspace{\fill}
  %\vspace{3cm}
  \subfloat[\centering VHDL]{{\includegraphics[trim=10 10 10 10,clip, width=0.45\textwidth]{img/matlab/lines_of_code_pie_chart_py_vhdl} }}%

@@

>>>>

\begin{figure}%
  \centering
  \subfloat[\centering Overview of ]{{\includegraphics[trim=10 10 10 10,clip, width=0.5\textwidth]{img/matlab/lines_of_code_pie_chart_py_all} }}%
  \\
  %\hspace{\fill}
  \subfloat[\centering HLS]{{\includegraphics[trim=10 10 10 10,clip, width=0.5\textwidth]{img/matlab/lines_of_code_pie_chart_py_hls} }}%
  %\hspace{\fill}
  %\vspace{3cm}
  \subfloat[\centering VHDL]{{\includegraphics[trim=10 10 10 10,clip, width=0.5\textwidth]{img/matlab/lines_of_code_pie_chart_py_vhdl} }}%

@@

Also note, that the common Python testbench consists of XXX lines of Python code.
Therefor, the testbench code of the respective IPs is relatively small, because the entire analysis part is shared.
